A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}

### 2019-12-04 1_intro.tex
clarify why wedge shape is representative (reviewer 1.6)
clarify contributions (reviewer 1.2)

\begin{figure}\centering
\setlength{\figwidth}{.9\columnwidth}
\setlength{\figwidthTwo}{.05\columnwidth}
\begin{subfigure}{\figwidth}\centering
\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_uniform}}\includegraphics[width=\figwidth]{sources-intro-TEST-naive-accuracy.png}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_centered}}\includegraphics[width=\figwidth]{sources-intro-TEST-Center-widths.png}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_distributed}}\includegraphics[width=\figwidth]{sources-intro-TEST-Distributed-widths.png}
\end{subfigure}
\caption{
Illustration of different toolpath for a wedge shape \revise{}{(black)}.
\subref{intro_wedge_uniform} Toolpath using uniform offsetting results in large overfill (orange) and underfill (azure).
\subref{intro_wedge_centered} Toolpath with adaptive width~\cite{Jin2017JMS} where beads that are wider or narrower than the nozzle size are indicatd in red and blue, respectively.
\subref{intro_wedge_distributed} Our approach minimizes over- and underfill with beads close to the nozzle size.
}
\label{intro_wedge}
\end{figure}

Our contributions are as follows:
\begin{itemize}
\item A geometric framework for generating densely filling contour-parallel toolpaths employing adaptive width, according to any beading scheme which decides on the bead spacing and widths.
\item A specific beading scheme for FDM printing which reduces the amount of deviation in the extrusion widths, and which promotes smooth toolpaths that are equal to the preferred width toward the outline of the shape.
\end{itemize}

>>>>

\begin{figure}\centering
\setlength{\figwidth}{.9\columnwidth}
\setlength{\figwidthTwo}{.05\columnwidth}
\begin{subfigure}{\figwidth}\centering
\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_uniform}}\includegraphics[width=\figwidth]{sources-intro-TEST-naive-accuracy.png}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_centered}}\includegraphics[width=\figwidth]{sources-intro-TEST-Center-widths.png}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_distributed}}\includegraphics[width=\figwidth]{sources-intro-TEST-Distributed-widths.png}
\end{subfigure}
\caption{
Illustration of different toolpath\revise{}{s} for a \revise{wedge }{}shape \revise{}{showcasing a range of shape radii }\revise{}{(black)}.
\subref{intro_wedge_uniform} Toolpath using uniform offsetting results in large overfill (orange) and underfill (azure).
\subref{intro_wedge_centered} Toolpath with adaptive width~\cite{Jin2017JMS} where beads that are wider or narrower than the nozzle size are indicatd in red and blue, respectively.
\subref{intro_wedge_distributed} Our approach minimizes over- and underfill with beads close to the nozzle size.
}
\label{intro_wedge}
\end{figure}

Our contributions are as follows:
\begin{itemize}
\item A geometric framework \revise{for generating densely filling contour-parallel toolpaths employing adaptive width, according to any beading scheme which decides on the bead spacing and widths.}{allowing various adaptive bead width control schemes used to generate contour-parallel toolpaths which minimize under- and overfill.}
\item A specific beading scheme for FDM printing which \revise{}{furthermore} reduces the amount of deviation in the extrusion widths compared to existing literature, and which \revise{promotes smooth toolpaths that are equal to the preferred width toward the outline of the shape.}{produces beads of exactly the preferred width outside of central regions of the outline shape.}
\end{itemize}
